% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\usepackage[paperwidth=21cm, paperheight=46cm, margin=1in]{geometry}

\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\begin{document}
% Center the name over the entire width of resume:
\moveleft.5\hoffset\centerline{\large\bf Cesar Kyle Casil}
\moveleft.5\hoffset\centerline{\small Software Developer}
\address{ Santa Clara, CA 95054 \\ cesarkylecasil@gmail.com  \\}
	\address{ \href{https://www.linkedin.com/in/ckcasil}{linkedin.com/in/ckcasil} \\ \href{https://www.github.com/ccasil}{github.com/ccasil} \\
	\href{https://www.cesarkylecasil.me}{cesarkylecasil.me} }

\begin{resume} 

% Draw a horizontal line the whole width of resume:
\moveleft\hoffset\vbox{\hrule width\resumewidth height 0.2pt}
\section{Summary} 
Cesar Kyle Casil is a Computer Science major from the University of California, Santa Cruz. He is currently practicing full stack web development in Python, iOS, and MEAN (MongoDB, Express, AngularJS, Node.js); he has experience in working with small teams using agile software programming. Since coming from both an accredited university and a coding bootcamp, he has not only acquired a unique set of skills, but has learned the importance of how they lead to success within the tech industry. His primary goal is to contribute his passion for programming towards a company's vision while expanding on his technical skills.

\section{Education}

\par
\textbf{University of California, Santa Cruz}\hfill Mar 2019\\
{\sl Bachelor of Science}, Computer Science

\par
\textbf{Coding Dojo}, Silicon Valley, CA\hfill Apr 2018\\
{\sl Certificate of Completion, Full Stack Developer}: Python, iOS, and MEAN (MongoDB, Express, Angular, Node.js) stack development
\begin{itemize} \itemsep -2pt  % reduce space between items
	\item Web development bootcamp specializing in front-end fundamentals as well as three full stacks. Dedicated over 1200+ hours of coding experience, including the ability to deploy a full website from client to server to database.
\end{itemize}

% Tabulate Computer Skills; p{3in} defines paragraph 3 inches wide
\section{Technical \\ Skills}
\begin{tabular}{l p{3.9in}}
	{\underline Languages:} & {\bf JavaScript} (ES6)/TypeScript, Swift 4, {\bf Python}, C, \LaTeX\\
	{\underline Front-End:} & {\bf HTML}, {\bf CSS}, {\bf jQuery}, AJAX, {\bf Bootstrap}, JSON, HTTP Request/Response\\
	{\underline Database:} & {\bf MySQL}, SQLite,{\bf PostgreSQL}, MongoDB, Mongoose.js, Django ORM, Core Data, {\bf CRUD operations}\\
	{\underline Frameworks and Libraries:} & {\bf Angular}, React, Node.js, Socket.IO, Express.js, Django, Flask\\
	{\underline Development Tools:} & {\bf Git}, Microsoft Visual Studio, Xcode, Amazon Web Services (EC2), NGINX, Postman, Node Package Manager (NPM)\\
	{\underline Miscellaneous:} & {\bf Agile Scrum Methodology}, {\bf Algorithms and Data Structures}, {\bf  Linux/Unix}, Software Deployment (AWS), RESTful Architecture/API, Object Oriented Programming (OOP), Model View Controller (MVC), Microsoft Office
\end{tabular}

\section{Experience}

\textbf{VeEX Inc.,} Web Development Engineer, Santa Clara, CA\hfill Apr 2019\textendash Present

Freelance Web Developer, Santa Clara, CA\hfill Jan 2018\textendash Jan 2019
\begin{itemize} \itemsep -2pt  % reduce space between items
	\item Building Full-Stack, modern, responsive web applications for clients while providing quick feedback and support
	\item Lead a small team to work with clients to create websites for various needs
\end{itemize}

\textbf{MissionU,} Research Intern, San Francisco, CA\hfill Mar 2017\textendash May 2017
\begin{itemize} \itemsep -2pt  % reduce space between items
	\item Collaborated in a small team to present a roadshow plan to reach out to local schools and community centers for brand launch
	\item Drafted 4 research documents from various sources that suggest 1.3 million new job postings in 2020 with skills in data science and analytics
	\item Curated 4 excel spreadsheets containing 151 subject matter experts, employer partner leads, and various professors to gain input on MissionU\textsc{\char13}s curriculum for the data analyst program
\end{itemize}

\textbf{Garcon LLC,} Android Developer Intern, Santa Clara, CA\hfill Sept 2016\textendash Dec 2016
\begin{itemize} \itemsep -2pt %reduce space between items
	\item Translated UI mockups into a working, interactive Android application using Android Studio and Java during its early stages
	\item Designed and created a functional implementation of the mobile application’s interface
	\item Testing and quality assurance
\end{itemize}

\section{Projects}

\href{https://github.com/ccasil/alextheparty}{\bf Alex the Party}\hfill Ongoing\\
E--commerce website selling photo prints. Takes customer from store front to cart to checkout.
\begin{itemize} \itemsep -2pt %reduce space between items
	\item \textbf{Technologies Used:} Angular, MongoDB, Express.js, Node.js, Bcrypt, Bootstrap, HTML5, CSS3, JavaScript, AWS (EC2), Responsive Wed Design (RWD)
\end{itemize}

\href{http://megumihfashion.com/}{\bf Megumi Hiramoto}\hfill Sept 2018\textendash Dec 2018\\
Portfolio for Academy of Art student to display her studies in Fashion Journalism.
\begin{itemize} \itemsep -2pt %reduce space between items
	\item \textbf{Technologies Used:} React, Bootstrap, HTML5, CSS3, JavaScript, Responsive Wed Design (RWD)
\end{itemize}

\href{http://lovechangingtheworld.org/}{\bf Love Changing the World, Inc.}\hfill Jun 2018\textendash Oct 2018\\
Public website for the non-profit organization Love Changing the World, Inc. Allows donations through PayPal in exchange for apparel with LCTW branding.
\begin{itemize} \itemsep -2pt %reduce space between items
	\item \textbf{Technologies Used:} React, Redux, MongoDB, Express, Node.js, Bootstrap, HTML5, CSS3, JavaScript, Google Maps API, PayPal API
\end{itemize}

\href{https://github.com/ccasil/GymLog}{\bf Gym Log}\hfill Apr 2018\\
Personal iOS application to aid in daily workout programs. Includes a user profile, kg/lb conversion calculator, and a log of main lifts.
\begin{itemize} \itemsep -2pt %reduce space between items
	\item \textbf{Technologies Used:} Xcode, Swift, Core Data, Auto Layout
\end{itemize}

\href{https://github.com/ccasil/geo_hack}{\bf Dojo Attendance Tracker}\hfill Mar 2018\\
iOS application that records the amount of time spent inside Coding Dojo as well as the time spent outside; can be expanded into an attendance tracker for Coding Dojo.
\begin{itemize} \itemsep -2pt %reduce space between items
	\item \textbf{Technologies Used:} Xcode, Swift, Core Location, Map Kit, AV Foundation, Core Data, Auto Layout
\end{itemize}

\href{https://github.com/ccasil/BRB31}{\bf Baskin Robbins Birthday 31}\hfill Feb 2018\\
Web application tailored to Baskin Robbins fans. Allows the user to view all flavor descriptions to be added as a favorite.
\begin{itemize} \itemsep -2pt %reduce space between items
	\item \textbf{Technologies Used:} Python, Django, SQLite3, Google Maps JavaScript API, Bcrypt, HTML5, CSS3, JavaScript, jQuery, Bootstrap, Object Relational Mapping (ORM), Object Oriented Programming (OOP)
\end{itemize}

\end{resume}
\end{document}